Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-14 exp1/present2013.tex
example -> block
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@667 43ef1190-90fd-4dd7-a769-d0121f02b80e
Fix date and shorttitle
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@668 43ef1190-90fd-4dd7-a769-d0121f02b80e
do some reformatting
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@669 43ef1190-90fd-4dd7-a769-d0121f02b80e

% set lecture number, date, title:
%\LectureNumber{13}
\LectureDate{23.10.2013}

@@

\title[Statistical Design]{Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation}
\subtitle{}
\author{Kjetil Kjernsmo and John Tyssedal}
\maketitle

@@

\begin{frame}{What's a benchmark?}

  \begin{itemize}
  \item Natural benchmarks.
  \item Benchmarking with broad and well-known workloads. 
  \item Use-case driven benchmarks.
  \end{itemize}

@@

% TODO Format well
   A \emph{response variable} is measured under various
    combinations of parameters.

For example:
\begin{itemize}
\item Throughput
\item Query execution time
\item Response time
\end{itemize}

@@

Such parameters are called \emph{factor}s.

For example:
\begin{itemize}
\item A concrete implementation
\item Hardware platform
\item Data heterogeneity
\item Number of triples in the store
\item Absence or presence of certain language features
\item Order of experiments
\item Tuning parameters
\item Concurrency
\end{itemize}

@@

For each factor, a range of possible values are fixed. These values
are called \emph{levels}.

\begin{block}
  For example:
  \begin{itemize}
  \item For implementation, 4store or Virtuoso.
  \item For number of triples, the levels could be 1 or 2 MTriples.
  \item For language features, the levels could be \textsf{SELECT} and \textsf{CONSTRUCT}
  \end{itemize}
\end{block}
Levels may be continuous, discrete, different instances of a
class, etc.

>>>>

% set lecture number, date, title:
%\LectureNumber{13}
\LectureDate{24.10.2013}

@@

\title[DoE in SPARQL Evaluations]{Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation}
\subtitle{}
\author{Kjetil Kjernsmo and John Tyssedal}
\maketitle

@@

\begin{frame}{Not all benchmarks are created equal}

  \begin{itemize}
  \item Natural benchmarks.
  \item Benchmarking with broad and well-known workloads. 
  \item Artificial use-case driven benchmarks.
  \end{itemize}

@@

 \Large
   A \emph{response variable} is measured under various
    combinations of parameters.
 \normalsize

    \begin{block}{Examples}
      \begin{itemize}
      \item Throughput
      \item Query execution time
      \item Response time
      \end{itemize}
    \end{block}

@@

\Large
Such parameters are called \emph{factor}s. 
\normalsize

\begin{block}{Examples}
  \begin{itemize}
  \item A concrete implementation
  \item Hardware platform
  \item Data heterogeneity
  \item Number of triples in the store
  \item Absence or presence of certain language features
  \item Order of experiments
  \item Tuning parameters
  \item Concurrency
  \end{itemize}
\end{block}

@@

\Large
For each factor, a range of possible values are fixed. These values
are called \emph{levels}.
\normalsize

\begin{block}{Examples}
  \begin{itemize}
  \item For implementation, 4store or Virtuoso.
  \item For number of triples, the levels could be 1 or 2 MTriples.
  \item For language features, the levels could be \textsf{SELECT} and \textsf{CONSTRUCT}
  \end{itemize}
\end{block}
Levels may be continuous, discrete, different instances of a
class, etc.
